CLT Results

### 2022-04-02 analysis/clt_data_processing.Rmd
add more data

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggpubr)
library(tidyboot)
library(readxl)
library(brms)
library(ggthemes)
library(writexl)
library(ggdist)
library(sf)
```

@@

# merge with aoa data
aoa <-  read_xlsx("../data/word_list.xlsx")%>%
  select(german,english, aoa_german_comb)%>%
  filter(german != "rakete")%>%
  rename(targetWord = english)%>%
  mutate(targetWord = ifelse(targetWord == "frying pan", "fryingpan", targetWord),
         targetWord = ifelse(targetWord == "courgette", "zucchini", targetWord),
         targetWord = ifelse(targetWord == "rocket", "arugula", targetWord),
         targetWord = ifelse(targetWord == "palm tree", "palmtree", targetWord))%>%
  filter(german != "kappe", 
         german != "karotte", 
         german != "mohrrübe")%>%
  distinct(german, .keep_all = T)%>%
  mutate(group = cut(aoa_german_comb, 
                   breaks=c(0, 3.5, 6, Inf), 
                   labels=c("low","middle","high")))

@@

```{r, warning=F}
files_zas <- str_subset(dir("../data/clt_raw_data_zas/", pattern = ".json"), pattern = "DELETE", negate = TRUE)

files_zas <- files_zas[!files_zas %in% pilot]

raw_data_zas <- data_frame()
for (f in files_zas) {
  jf <- paste("../data/clt_raw_data_zas/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  subjID <- jd$meta$subjID
  order <- jd$meta$order
  add <- as_data_frame(jd$data) %>% mutate(subjID = subjID,
                                                 order = order)
  raw_data_zas <- bind_rows(raw_data_zas, add)
}

proc_data_zas <- raw_data_zas%>%
  mutate(subjID2 = subjID)%>%
  separate(subjID2, into = c("bday","sex","postcode"), sep="_")%>%
  mutate(test_day = substr(timestamp, 0,10),
         test_day = as.Date(test_day,"%Y-%m-%d"),
         bday  = as.Date(bday,"%d-%m-%Y"),
         age = as.numeric(difftime(test_day, bday, units = "days"))/365.25,
         sex = tolower(sex))

data_zas <- proc_data_zas%>%
  left_join(aoa)%>%
  select(-timestamp)%>%
  ungroup()%>%
  mutate(age_group = substr(age,0,1))%>%
  select(-bday, -test_day)%>%
  filter(!is.na(age))%>%
  ungroup()

@@

```{r}
p1 <- data%>%
  group_by(targetWord, aoa_german_comb)%>%
  tidyboot_mean(col = correct)

ggplot(p1, aes(x = aoa_german_comb, y = mean))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r", label.y = 0.85)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75)+
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm")+
  labs(x = "Rated age of acquisition", y = "Proportion correct")+
  ylim(0,1)+
  theme_minimal()
```

@@

```{r}
p1_1 <- data%>%
  group_by(targetWord, order)%>%
  tidyboot_mean(col = correct)

@@

ggplot(p1_2, aes(x = mean_orderA, y = mean_orderB))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r")+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  #geom_hline(yintercept = 0.25, alpha = .5)+
  #geom_vline(xintercept = 0.25, alpha = .5)+
  geom_errorbar(aes(xmin = ci_lower_orderA, xmax = ci_upper_orderA), alpha = .5)+
  geom_errorbar(aes(ymin = ci_lower_orderB, ymax = ci_upper_orderB), alpha = .5)+
  geom_point( size =2, stroke = 1, alpha= .75)+
  labs(x = "Order A", y = "Order B")+
  ylim(0,1)+
  xlim(0,1)+
  theme_minimal()
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggpubr)
library(tidyboot)
library(readxl)
library(brms)
library(ggthemes)
library(writexl)
library(ggdist)
library(sf)
library(geomtextpath)
```

@@

# merge with aoa data
aoa <-  read_xlsx("../data/word_list.xlsx")%>%
  select(german,english, aoa_german_comb)%>%
  filter(german != "rakete",
         german != "hobel")%>%
  rename(targetWord = english)%>%
  mutate(targetWord = ifelse(targetWord == "frying pan", "fryingpan", targetWord),
         targetWord = ifelse(targetWord == "courgette", "zucchini", targetWord),
         targetWord = ifelse(targetWord == "rocket", "arugula", targetWord),
         targetWord = ifelse(targetWord == "palm tree", "palmtree", targetWord),
         targetWord = ifelse(targetWord == "airplane", "plane", targetWord))%>%
  filter(german != "kappe", 
         german != "karotte", 
         german != "mohrrübe")%>%
  distinct(german, .keep_all = T)%>%
  mutate(group = cut(aoa_german_comb, 
                   breaks=c(0, 3.5, 6, Inf), 
                   labels=c("low","middle","high")))

@@

```{r, warning=F}
# files_zas <- str_subset(dir("../data/clt_raw_data_zas/", pattern = ".json"), pattern = "DELETE", negate = TRUE) 
# 
# files_zas <- files_zas[!files_zas %in% pilot]
# 
# raw_data_zas <- data_frame()
# for (f in files_zas) {
#   jf <- paste("../data/clt_raw_data_zas/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   subjID <- jd$meta$subjID
#   order <- jd$meta$order
#   add <- as_data_frame(jd$data) %>% mutate(subjID = subjID,
#                                                  order = order)
#   raw_data_zas <- bind_rows(raw_data_zas, add)
# }
# 
# proc_data_zas <- raw_data_zas%>%
#   mutate(subjID2 = subjID)%>%
#   separate(subjID2, into = c("bday","sex","postcode"), sep="_")%>%
#   mutate(test_day = substr(timestamp, 0,10),
#          test_day = as.Date(test_day,"%Y-%m-%d"),
#          bday  = as.Date(bday,"%d-%m-%Y"),
#          age = as.numeric(difftime(test_day, bday, units = "days"))/365.25,
#          sex = tolower(sex))
# 
# data_zas <- proc_data_zas%>%
#   left_join(aoa)%>%
#   select(-timestamp)%>%
#   ungroup()%>%
#   mutate(age_group = substr(age,0,1))%>%
#   select(-bday, -test_day)%>%
#   filter(!is.na(age))%>%
#   ungroup()

@@

```{r}
p1 <- data%>%
  group_by(targetWord, aoa_german_comb, german)%>%
  tidyboot_mean(col = correct)

ggplot(p1, aes(x = aoa_german_comb, y = mean))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r", label.y = 0.85)+
  geom_hline(yintercept = 0.25, lty = 3, alpha = .75)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = .75)+
  geom_textpath(aes(label = german), hjust = -.2) +
  #geom_point( alpha = .75)+
  geom_smooth(method = "lm")+
  labs(x = "Rated age of acquisition", y = "Proportion correct")+
  ylim(0,1)+
  theme_minimal()
```

@@

```{r}
p1_1 <- data%>%
  group_by(targetWord,german, order)%>%
  tidyboot_mean(col = correct)

@@

ggplot(p1_2, aes(x = mean_orderA, y = mean_orderB))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r")+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  geom_textpath(aes(label = german), hjust = -.2) +
  #geom_hline(yintercept = 0.25, alpha = .5)+
  #geom_vline(xintercept = 0.25, alpha = .5)+
  geom_errorbar(aes(xmin = ci_lower_orderA, xmax = ci_upper_orderA), alpha = .5)+
  geom_errorbar(aes(ymin = ci_lower_orderB, ymax = ci_upper_orderB), alpha = .5)+
  geom_point( size =2, stroke = 1, alpha= .75)+
  labs(x = "Order A", y = "Order B")+
  ylim(0,1)+
  xlim(0,1)+
  theme_minimal()
```
